### 2024-03-21 Paper/paper.tex
Added paper and presentation .tex

\documentclass[12pt]{article}
\usepackage{fancyhdr}     % Enhanced control over headers and footers 
\usepackage[T1]{fontenc}  % Font encoding
\usepackage{mathptmx}     % Choose Times font 
\usepackage{microtype}    % Improves line breaks      
\usepackage{setspace}     % Makes the document look like horse manure 
\usepackage{hyperref}
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = black, %Colour of internal links
	citecolor   = black %Colour of citations
}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{endnotes}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage{rotating}

\usepackage[style=apa,backend=biber,citestyle=numeric]{biblatex}
\addbibresource{../refs.bib}

\title{Merkle Trees}
\author{Taylor Blair}
\date{\today}
\let\footnote=\endnote

\usepackage{verbatim}

\pagestyle{fancy} % Default page style 
\lhead{Taylor Blair}
\chead{}
\rhead{\thepage}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\renewcommand{\theendnote}{\Roman{endnote}}

\begin{document}
\doublespacing
\maketitle

\begin{abstract}
	Merkle trees are secured data structures whose operations generate proofs that use $\mathcal{O}(\log(n))$ hashes. The runtime complexity combined with other properties related to trees makes it a useful component in several open-source projects.
\end{abstract}

\tableofcontents

\section{Introduction}

Merkle trees were invented by Ralph Merkle. Ralph Merkle initially patented Merkle trees for digital signatures. After the patent expired Merkle trees were implemented in a variety of open source projects.

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
	\caption{Basic Merkle Tree\cite{wikipedia-merkle-tree}}
\end{figure}

Merkle trees are a data structure where the node values represent a hash of the nodes below. They have several desirable properties related to the runtime of operations on the Merkle trees.

The security of Merkle trees is related to the ability to collide against the hash function. As such, a strong hash function is required for constructing the Merkle trees.

\subsection{History}

\begin{figure}[H]
	\begin{tikzpicture}[scale=0.5,every node/.style={outer sep=5pt}]
		%Notation: {year, the title of the event}
		%NOTE! Everyting is zero-based
		\def\ourInfo{{
				{"1987"," The patent a 'Method of providing digital signatures' is filed by Ralph C. Merkle\cite{merkle-patent}."},
				{"1999","The original patent expires."},
				{"2009","Bitcoin uses Merkle Trees for 'block header commitment.'\cite{friedenbach_alm_2017}"},			
				{"2009","BitTorent uses Merkle Trees for data integrity\cite{bep30}."},
		}}
		\pgfmathsetmacro{\length}{3}% Zero based.

		% Loop through the array containing all events.
		\foreach \i in {0, ..., \length}{
			\pgfmathsetmacro{\year}{\ourInfo[\i][0]}% Get the left cell (year)
			\pgfmathsetmacro{\eventName}{\ourInfo[\i][1]}% Get the right cell (event name)
			\draw[thick,red] (0,-2*\i-2)--(0,-2*\i);% Draw vertical line
			\ifnum \i=0 % Should be in red text
			\draw(0,-2*\i-1) node[black, right, align = left]{\eventName};% Display the event name
			\draw(0,-2*\i-1) node[black, left] {\year};
			\else % Should be in black text
			\draw(0,-2*\i-1) node[right, black]{\eventName};% Display the event name
			\draw(0,-2*\i-1) node[left] {\year};% Display the year
			\fi
		}
		% Draw the bullet with the dash
		\foreach \i in {0, ..., \length}{
			\filldraw[draw = white, fill = red,thick] (0,-2*\i-1) circle (5pt);
			\draw[thick,red] (-12pt,-2*\i-1)--(0,-2*\i-1);
		}
	\end{tikzpicture}
\end{figure}

As stated above, Merkle trees were created in 1987 by Ralph Merkle for digital signatures\cite{merkle-patent}. In the initial patent, the nodes were used for signing and verification:

\begin{quote}
	To sign a message $M_i$ the signer selects a previously unused node (i.e., node $i$) from the infinite tree. The message signing key at this node is then used to sign this message. The sequence of nodes from the root of the tree (i.e., node 1) to node $i$ is then used to verify that the message signature is correct and has not been tampered with.\cite{merkle-patent}
\end{quote}

Once the Merkle tree patent expired Merkle trees were implemented in various open-source projects including Bitcoin and BitTorrent which is expanded upon in a section below.

\section{Literature Review}

Merkle Trees are a component of several projects, as such many papers provide incremental changes towards certain operations on Merkle trees. This paper references the original patent by Ralph Merkle \cite{merkle-patent} in addition to descriptions of Merkle tree operations given by Boneh and Shoup \cite{boneh2020graduate}. As secondary sources, the implementation of Merkle trees in Bitcoin \cite{friedenbach_alm_2017} provides a real example of the impact of hash functions in addition to a whitepaper from the BitTorrent project\cite{bep30}.

\section{Construction}
 Merkle trees are constructed from the bottom up by hashing data as the leaf nodes.

 \begin{algorithm}[H]
 	\caption{Merkle tree construction}
 	\begin{algorithmic}
 		\For{$i = 1,\ldots, n$} \Comment{Compute leaf node hashes}
 		\State $y_i \leftarrow h(x_i)$  
 		\EndFor
 		 \For{$j= 1,\ldots, n-1$}  \Comment{Compute intermediate Nodes from $y_{n+1}, \ldots , y_{2n -1}$}
 		\State $y_{i+n} \leftarrow h(y_{2i-1}, y_{2i}) $ \Comment{Hash leaf nodes below for new hash}
 		\EndFor
 		\State \Return $Y$ \Comment{Return tree where $y_{2n-1}$ is the root}
 	\end{algorithmic}
 \end{algorithm}

When referring to the parts of a Merkle tree the most common terminology is "root hash" which refers to the hashed value of the root of the tree and "leaf hash" which refers to the hash for a given data block.

\section{Operations}

There are several operations can for Merkle trees unrelated to tree manipulation that generate a proof resulting in a root hash. The root hash from the proof is then verified against a known hash to check for correctness. The most common operations are as follows.

\subsection{Proving Equality of Merkle Trees}

\begin{figure}[H]
	\begin{center}
		\begin{verbatim}
    ROOT1              ROOT2
   /     \             /     \
  L1       R1         L2      R2
 /  \    /  \        /  \    /  \     
L1.1  ....  R1.2    L2.1 ... R2.2
		\end{verbatim}
	\end{center}
\end{figure}

Proving the equality of two Merkle trees is an $O(1)$ operation. The operation compares the root nodes of the two trees. If the root nodes match, then the trees are equal.

\subsection{Proving Membership}

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
	\caption{Show "\textit{Germany}" exist in the tree\cite{buchannen_2022}}
	% The reason we only need nodes 1, 34 and 567, is that we can regenerate Node 12 and Node 1234 from these values. Bitcoin, for example, uses this method in order to check the validity of a transaction within the block. We can then add our transactions into a Merkle Tree, and produce a root hash. Within the block we can then add the root hash of the previous block and the root hash of the next block, and thus interlock the blocks into a chain:	
\end{figure}

Using the figure above as an example, to prove  "\textit{Germany}" is a member of the tree the verifier hashes "\textit{Germany}" and hashes it with its sibling node to find the parent node. The parent node is then hashed with its sibling and the process repeats until the root node. The generated root node is compared with the known root node, should the hashes match then the element is verified. Proving membership requires checking $\log(n)$ tree levels, thus the operation takes $O(\log(n))$ time.

Another advantage to checking membership using a Merkle tree is that checking the membership of multiple leaf nodes can be done in $O(\log(n))$. In the example above by proving "\emph{Germany}" was a member of the tree, the verifier also verified that "\emph{France}" was a member of the tree.

\subsection{Proving Non-Membership}

	\begin{figure}[H]
		\centering
	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
	\caption{Show $x$ is not in the tree\cite{boneh2020graduate}}
	%possible.
\end{figure}

While hashing a value and checking if it appears in the leaf nodes might appear to Non membership cannot be verified using a standard Merkle tree. Non membership can only be proven with a sorted Merkle tree.  Dan Boneh and Victor Shoup provide the following  algorithm:
\begin{quote}
	To produce the proof, the prover first locates the two adjacent leaves $x_i$ and $x_{i+1 }$in T that bracket $x$, namely $x_i < x < x_{i+1}$. Next, the prover provides a Merkle proof that $x_i$
	is in position $i$ in $T$, and that $x_{i+1}$ is in position $i + 1$ in $T$. The verifier can check that these two leaves
	are adjacent, and that $x_i < x < x_{i+1}$, and this proves that $x$ is not in $T$. 
	\end{quote}

This operation takes $O(\log(n))$, but the additional requirement that the Merkle tree be sorted limits what operations can be used on the Merkle tree, notably merging.

\subsection{Merging Merkle Trees}

\begin{figure}[H]
    \begin{center}
	\begin{verbatim}
             ROOT
             /   \
           /       \
         /           \
       /               \
     ROOT1              ROOT2
   /     \             /     \
 L1       R1         L2      R2
 /  \    /  \       /  \    /  \     
L1.1  ....  R1.2   L2.1   ...   R2.2
\end{verbatim}
 \end{center}
\end{figure}

Merging Merkle trees is an $O(1)$ operation of the root of two other Merkle trees and creates a new root node. This operation can be used to add individual nodes to a Merkle tree, but it creates an unbalanced tree.

\section{Security}

\subsection{Authenticated Data Structure}

As defined by Boneh and Soup, Merkle Trees are secure data structures composed of three algorithms $D = (H, P, V )$\cite{boneh2020graduate}:
\begin{itemize}
	\item $H$ a secure hash function
	\item $P$ a proof function that takes an element, location, and structure $(i, x, T)$ and returns a proof of a given element
	\item $V$ a verification algorithm $V (i, x, y, \pi)$ that "accepts" or "rejects" a proof.
\end{itemize}

\subsection{Merkle Tree Attack Game}

The attack game for Merkle trees is defined in Boneh and Shoup using the definition of an authenticated data structure. Given a Merkle tree $D = (H, P, V )$ defined over $(\mathcal{X}^{n}, \mathcal{Y})$, and a given adversary $\mathcal{A}$:

\begin{quote}
	The adversary $A$ outputs a $y \in \mathcal{Y}$, a position $i \in \{1, \ldots , n\}$, and two pairs $(x, \pi)$ and $(x', \pi')$ where $x, x' \in \mathcal{X}$.
\end{quote}

$\mathcal{A}$ wins the game if $x \neq x'$ and $V(i, x, y, \pi)=V(i, x', y, \pi')=$accept. Define $\mathcal{A}$'s advantage with respect to $\mathcal{D}$, denoted $\mathrm{ADSadv}[\mathcal{A}, \mathcal{D}]$, as the probability that $\mathcal{A}$ wins the game\cite{boneh2020graduate}.

\subsection{Security Proof}

Using the definition of the authenticated data structure combined with the attack game above, the security of the Merkle tree is dependent on the underlying hash function.

The goal of the attacker is to generate a proof of membership at a given location. This can be reduced to creating a hash collision where the root node will be the same.

In the case of a Merkle tree with only one leaf node, the attacker would need to generate a collision $c$ such that if $H(x) = x'$, then $H(c)=x'$ but $x\neq c$.

In the case of a Merkle tree with two leaf nodes, the attacker can create a collision by colliding on the hash of the leaf node or by colliding against the root node. Let $a, b$ be the data blocks and let $H(a)=a', H(b)=b'$ which gives a root node $H(a'b')=r$. The attacker can either find $H(c)=c'$ such that $c' = a'$, $c'=b'$ or $H(c'b') = r$, $H(a'c') = r$. All attacks depend on a flaw in the hash function.

More generally, $x \in T$ with hash $H(x) = h$ at position $i$. Let the attacker create a collision such that $H(y) = h$ but $x \neq y$. Thus the attacker's advantage against a Merkle tree is the same as the attacker's advantage against the hash function used by the Merkle tree.

\section{Use Cases}

Merkle trees are used as authenticated data structures with optimal complexity for proving membership and comparing against other structures.

\subsection{Bitcoin} \label{sec:Bitcoin}

Bitcoin, and other cryptocurrencies, use Merkle trees for the commitment header.  The \textit{chain} in blockchain refers to the chain of receipts from processed transactions. It would be too slow to create a receipt for each transaction, so Bitcoin groups transactions into sections. The smaller group of transactions is a Merkle tree where the leaf nodes represent a single transaction. Thus the group of transactions results in a root hash which is used as the commitment header.

Merkle trees were incorrectly implemented in the Bitcoin protocol. This implementation resulted in DOS attacks due to over-hashing and duplicate nodes (CVE-2012-2459). This bug was patched in a proposal that replaced the Merkle tree implementation\cite{friedenbach_alm_2017}.

\subsection{BitTorrent Data Integrity} \label{sec:BitTorrent}

BitTorrent uses Merkle trees for checking the integrity of torrented files. The torrented data is hashed into a Merkle Tree and the root hash is compared with a trusted peer to verify integrity\cite{bep30}. If the root hashes do not match then the nodes below are compared with the trusted peer. This process repeats until a non-matching block is reached. The advantage of using a Merkle tree over another data structure is finding corrupted data blocks in $O(\log(n))$ time.

\section{Closing}

Merkle trees were not the first authenticated data structure, the Merkle Damgard construction provides several of the same operations \cite{boneh2020graduate}, but the number of properties in Merkle trees makes them desirable across a multitude of applications. The core construct of Merkle Trees, the tree, enables $O(\log (n))$  time operations in addition to speed-ups for proofs of many members. Their usage in various applications, notably in most cryptocurrencies, serves as evidence that Merkle trees will continue to propagate.

\newpage

\printbibliography

\end{document}

### 2024-03-21 Paper/paper.tex
Removed some of the previous work

@@
 
-\title{Merkle Trees}
-\author{Taylor Blair}
+\title{Bayesian Neural Networks}
+\author{
+	Blair, Taylor\\
+	\and
+	Ava\\
+	\and
+	Conor\\
+}
 \date{\today}
@@
 \begin{abstract}
-	Merkle trees are secured data structures whose operations generate proofs that use $\mathcal{O}(\log(n))$ hashes.
-The runtime complexity combined with other properties related to trees makes it a useful component in several open-source projects.
+	Bayesian Neural Networks are...
 \end{abstract}
@@
 
-Merkle trees were invented by Ralph Merkle.
-Ralph Merkle initially patented Merkle trees for digital signatures.
-After the patent expired Merkle trees were implemented in a variety of open source projects.
+\subsection{Neural Networks}
+
+\subsection{Bayesian Neural Networks}
+
+Bayesian Neural were invented by Ralph Merkle. Ralph Merkle initially patented Merkle trees for digital signatures....
 
@@
 
-Merkle trees are a data structure where the node values represent a hash of the nodes below. They have several desirable properties related to the runtime of operations on the Merkle trees.
-
-The security of Merkle trees is related to the ability to collide against the hash function. As such, a strong hash function is required for constructing the Merkle trees.
+....
 
@@
 
-As stated above, Merkle trees were created in 1987 by Ralph Merkle for digital signatures\cite{merkle-patent}. In the initial patent, the nodes were used for signing and verification:
-
-\begin{quote}
-	To sign a message $M_i$ the signer selects a previously unused node (i.e., node $i$) from the infinite tree.
-The message signing key at this node is then used to sign this message.
-The sequence of nodes from the root of the tree (i.e., node 1) to node $i$ is then used to verify that the message signature is correct and has not been tampered with.\cite{merkle-patent}
-\end{quote}
-
-Once the Merkle tree patent expired Merkle trees were implemented in various open-source projects including Bitcoin and BitTorrent which is expanded upon in a section below.
-
 \section{Literature Review}
@@
 
-\section{Operations}
-
-There are several operations can for Merkle trees unrelated to tree manipulation that generate a proof resulting in a root hash.
-The root hash from the proof is then verified against a known hash to check for correctness.
-The most common operations are as follows.
-
-\subsection{Proving Equality of Merkle Trees}
-
-\begin{figure}[H]
-	\begin{center}
-		\begin{verbatim}
-    ROOT1              ROOT2
-   /     \             /     \
-  L1       R1         L2      R2
- /  \    /  \        /  \    /  \     
-L1.1  ....  R1.2    L2.1 ... R2.2
-		\end{verbatim}
-	\end{center}
-\end{figure}
-
-Proving the equality of two Merkle trees is an $O(1)$ operation. The operation compares the root nodes of the two trees. If the root nodes match, then the trees are equal.
-
-\subsection{Proving Membership}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
-	\caption{Show "\textit{Germany}" exist in the tree\cite{buchannen_2022}}
-	% The reason we only need nodes 1, 34 and 567, is that we can regenerate Node 12 and Node 1234 from these values.
-Bitcoin, for example, uses this method in order to check the validity of a transaction within the block.
-We can then add our transactions into a Merkle Tree, and produce a root hash.
-Within the block we can then add the root hash of the previous block and the root hash of the next block, and thus interlock the blocks into a chain:
-\end{figure}
-
-Using the figure above as an example, to prove  "\textit{Germany}" is a member of the tree the verifier hashes "\textit{Germany}" and hashes it with its sibling node to find the parent node.
-The parent node is then hashed with its sibling and the process repeats until the root node.
-The generated root node is compared with the known root node, should the hashes match then the element is verified.
-Proving membership requires checking $\log(n)$ tree levels, thus the operation takes $O(\log(n))$ time.
-
-Another advantage to checking membership using a Merkle tree is that checking the membership of multiple leaf nodes can be done in $O(\log(n))$.
-In the example above by proving "\emph{Germany}" was a member of the tree, the verifier also verified that "\emph{France}" was a member of the tree.
-
-\subsection{Proving Non-Membership}
-
-	\begin{figure}[H]
-		\centering
-	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
-	\caption{Show $x$ is not in the tree\cite{boneh2020graduate}}
-	%possible.
-\end{figure}
-
-While hashing a value and checking if it appears in the leaf nodes might appear to Non membership cannot be verified using a standard Merkle tree.
-Non membership can only be proven with a sorted Merkle tree.
-Dan Boneh and Victor Shoup provide the following  algorithm:
-\begin{quote}
-	To produce the proof, the prover first locates the two adjacent leaves $x_i$ and $x_{i+1 }$in T that bracket $x$, namely $x_i < x < x_{i+1}$. Next, the prover provides a Merkle proof that $x_i$
-	is in position $i$ in $T$, and that $x_{i+1}$ is in position $i + 1$ in $T$. The verifier can check that these two leaves
-	are adjacent, and that $x_i < x < x_{i+1}$, and this proves that $x$ is not in $T$. 
-	\end{quote}
-
-This operation takes $O(\log(n))$, but the additional requirement that the Merkle tree be sorted limits what operations can be used on the Merkle tree, notably merging.
-
-\subsection{Merging Merkle Trees}
-
-\begin{figure}[H]
-    \begin{center}
-	\begin{verbatim}
-             ROOT
-             /   \
-           /       \
-         /           \
-       /               \
-     ROOT1              ROOT2
-   /     \             /     \
- L1       R1         L2      R2
- /  \    /  \       /  \    /  \     
-L1.1  ....  R1.2   L2.1   ...   R2.2
-\end{verbatim}
- \end{center}
-\end{figure}
-
-Merging Merkle trees is an $O(1)$ operation of the root of two other Merkle trees and creates a new root node.
-This operation can be used to add individual nodes to a Merkle tree, but it creates an unbalanced tree.
-
-\section{Security}
-
-\subsection{Authenticated Data Structure}
-
-As defined by Boneh and Soup, Merkle Trees are secure data structures composed of three algorithms $D = (H, P, V )$\cite{boneh2020graduate}:
-\begin{itemize}
-	\item $H$ a secure hash function
-	\item $P$ a proof function that takes an element, location, and structure $(i, x, T)$ and returns a proof of a given element
-	\item $V$ a verification algorithm $V (i, x, y, \pi)$ that "accepts" or "rejects" a proof.
-\end{itemize}
-
-\subsection{Merkle Tree Attack Game}
-
-The attack game for Merkle trees is defined in Boneh and Shoup using the definition of an authenticated data structure.
-Given a Merkle tree $D = (H, P, V )$ defined over $(\mathcal{X}^{n}, \mathcal{Y})$, and a given adversary $\mathcal{A}$:
-
-\begin{quote}
-	The adversary $A$ outputs a $y \in \mathcal{Y}$, a position $i \in \{1, \ldots , n\}$, and two pairs $(x, \pi)$ and $(x', \pi')$ where $x, x' \in \mathcal{X}$.
-\end{quote}
-
-$\mathcal{A}$ wins the game if $x \neq x'$ and $V(i, x, y, \pi)=V(i, x', y, \pi')=$accept.
-Define $\mathcal{A}$'s advantage with respect to $\mathcal{D}$, denoted $\mathrm{ADSadv}[\mathcal{A}, \mathcal{D}]$, as the probability that $\mathcal{A}$ wins the game\cite{boneh2020graduate}.
-
-\subsection{Security Proof}
-
-Using the definition of the authenticated data structure combined with the attack game above, the security of the Merkle tree is dependent on the underlying hash function.
-
-The goal of the attacker is to generate a proof of membership at a given location. This can be reduced to creating a hash collision where the root node will be the same.
-
-In the case of a Merkle tree with only one leaf node, the attacker would need to generate a collision $c$ such that if $H(x) = x'$, then $H(c)=x'$ but $x\neq c$.
-
-In the case of a Merkle tree with two leaf nodes, the attacker can create a collision by colliding on the hash of the leaf node or by colliding against the root node.
-Let $a, b$ be the data blocks and let $H(a)=a', H(b)=b'$ which gives a root node $H(a'b')=r$.
-The attacker can either find $H(c)=c'$ such that $c' = a'$, $c'=b'$ or $H(c'b') = r$, $H(a'c') = r$.
-All attacks depend on a flaw in the hash function.
-
-More generally, $x \in T$ with hash $H(x) = h$ at position $i$.
-Let the attacker create a collision such that $H(y) = h$ but $x \neq y$.
-Thus the attacker's advantage against a Merkle tree is the same as the attacker's advantage against the hash function used by the Merkle tree.
+\section{How it works}
 
@@
 
+\section{Simulation}
+
+We used the Cifar 10....
+
 \section{Closing}
-
-Merkle trees were not the first authenticated data structure, the Merkle Damgard construction provides several of the same operations \cite{boneh2020graduate}, but the number of properties in Merkle trees makes them desirable across a multitude of applications.
-The core construct of Merkle Trees, the tree, enables $O(\log (n))$  time operations in addition to speed-ups for proofs of many members.
-Their usage in various applications, notably in most cryptocurrencies, serves as evidence that Merkle trees will continue to propagate.
 

### 2024-03-21 Paper/paper.tex
Removing old work

@@
 \usepackage{algpseudocode}
-
 \usepackage{multicol}
@@
 \author{
-	Blair, Taylor\\
+	Blair, Taylor
 	\and
-	Ava\\
+	Sorgmon, Ava
 	\and
-	Conor\\
+	Conor
 }
@@
 \pagestyle{fancy} % Default page style 
-\lhead{Taylor Blair}
+\lhead{Blair, Sorgman, Conor}
 \chead{}
@@
 
-Merkle trees are used as authenticated data structures with optimal complexity for proving membership and comparing against other structures.
-
-\subsection{Bitcoin} \label{sec:Bitcoin}
-
-Bitcoin, and other cryptocurrencies, use Merkle trees for the commitment header.
-The \textit{chain} in blockchain refers to the chain of receipts from processed transactions.
-It would be too slow to create a receipt for each transaction, so Bitcoin groups transactions into sections.
-The smaller group of transactions is a Merkle tree where the leaf nodes represent a single transaction.
-Thus the group of transactions results in a root hash which is used as the commitment header.
-
-Merkle trees were incorrectly implemented in the Bitcoin protocol.
-This implementation resulted in DOS attacks due to over-hashing and duplicate nodes (CVE-2012-2459).
-This bug was patched in a proposal that replaced the Merkle tree implementation\cite{friedenbach_alm_2017}.
-
-\subsection{BitTorrent Data Integrity} \label{sec:BitTorrent}
-
-BitTorrent uses Merkle trees for checking the integrity of torrented files.
-The torrented data is hashed into a Merkle Tree and the root hash is compared with a trusted peer to verify integrity\cite{bep30}.
-If the root hashes do not match then the nodes below are compared with the trusted peer.
-This process repeats until a non-matching block is reached.
-The advantage of using a Merkle tree over another data structure is finding corrupted data blocks in $O(\log(n))$ time.
+...
 

### 2024-03-25 Paper/paper.tex
Updated presentation

@@
 
+Neural networks....
+
+\subsection{Convolutional Neural Networks }
+
+Convolutional neural networks are a type of neural network that is better suited for
+
 \subsection{Bayesian Neural Networks}
@@
 
-Merkle Trees are a component of several projects, as such many papers provide incremental changes towards certain operations on Merkle trees.
-This paper references the original patent by Ralph Merkle \cite{merkle-patent} in addition to descriptions of Merkle tree operations given by Boneh and Shoup \cite{boneh2020graduate}.
-As secondary sources, the implementation of Merkle trees in Bitcoin \cite{friedenbach_alm_2017} provides a real example of the impact of hash functions in addition to a whitepaper from the BitTorrent project\cite{bep30}.
-
-\section{Construction}
- Merkle trees are constructed from the bottom up by hashing data as the leaf nodes.
-
- \begin{algorithm}[H]
- 	\caption{Merkle tree construction}
- 	\begin{algorithmic}
- 		\For{$i = 1,\ldots, n$} \Comment{Compute leaf node hashes}
- 		\State $y_i \leftarrow h(x_i)$  
- 		\EndFor
- 		 \For{$j= 1,\ldots, n-1$}  \Comment{Compute intermediate Nodes from $y_{n+1}, \ldots , y_{2n -1}$}
- 		\State $y_{i+n} \leftarrow h(y_{2i-1}, y_{2i}) $ \Comment{Hash leaf nodes below for new hash}
- 		\EndFor
- 		\State \Return $Y$ \Comment{Return tree where $y_{2n-1}$ is the root}
- 	\end{algorithmic}
- \end{algorithm}
-
-When referring to the parts of a Merkle tree the most common terminology is "root hash" which refers to the hashed value of the root of the tree and "leaf hash" which refers to the hash for a given data block.
-
 \section{How it works}
@@
 
-We used the Cifar 10....
+We use a bayesian convolutional neural network implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ...
+\cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}
 

### 2024-03-25 Paper/paper.tex
Updated paper

@@
 
-\subsection{Neural Networks}
-
-Neural networks....
-
-\subsection{Convolutional Neural Networks }
-
-Convolutional neural networks are a type of neural network that is better suited for
-
-\subsection{Bayesian Neural Networks}
-
-Bayesian Neural were invented by Ralph Merkle. Ralph Merkle initially patented Merkle trees for digital signatures....
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=.8\textwidth]{../Images/merkle-example.png}
-	\caption{Basic Merkle Tree\cite{wikipedia-merkle-tree}}
-\end{figure}
-
-....
-
 \subsection{History}
@@
 
-\section{Literature Review}
+\section{Neural Network}
 
-\section{How it works}
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}
+		% Define node styles
+		\tikzstyle{neuron} = [circle, draw, minimum size=1.5cm];
+		\tikzstyle{weight} = [font=\scriptsize];
 
-\section{Use Cases}
+		% Input layer (2 neurons)
+		\node[neuron] (input1) at (-2,1) {Input 1};
+		\node[neuron] (input2) at (-2,-1) {Input 2};
 
-...
+		% Hidden layer (3 neurons)
+		\node[neuron] (hidden1) at (2,2) {Hidden 1};
+		\node[neuron] (hidden2) at (2,0) {Hidden 2};
+		\node[neuron] (hidden3) at (2,-2) {Hidden 3};
+
+		% Output layer (2 neurons for classification)
+		\node[neuron] (output1) at (6,1) {Class 1};
+		\node[neuron] (output2) at (6,-1) {Class 2};
+
+		% Connections with weights
+		\draw[->] (input1) -- node[weight, above] {$w_{1,1}$} (hidden1);
+		\draw[->] (input2) -- node[weight, above] {$w_{2,1}$} (hidden1);
+		\draw[->] (input1) -- node[weight, right] {$w_{1,2}$} (hidden2);
+		\draw[->] (input2) -- node[weight, right] {$w_{2,2}$} (hidden2);
+		\draw[->] (input1) -- node[weight, above] {$w_{1,3}$} (hidden3);
+		\draw[->] (input2) -- node[weight, above] {$w_{2,3}$} (hidden3);
+		\draw[->] (hidden1) -- node[weight, right] {$v_{1,1}$} (output1);
+		\draw[->] (hidden2) -- node[weight, right] {$v_{2,1}$} (output1);
+		\draw[->] (hidden3) -- node[weight, right] {$v_{3,1}$} (output1);
+		\draw[->] (hidden1) -- node[weight, above] {$v_{12}$} (output2);
+		\draw[->] (hidden2) -- node[weight, above] {$v_{2,2}$} (output2);
+		\draw[->] (hidden3) -- node[weight, above] {$v_{3,2}$} (output2);
+	\end{tikzpicture}
+	\caption{Example neural network}
+\end{figure}
+
+Neural networks....
+
+\subsection{Convolutional Neural Networks }
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=.8\textwidth]{../Images/big-pic-cnn.jpg}
+	\caption{CNN pipeline \cite{eli5CNN}}
+\end{figure}
+
+Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition. Instead of reading the entire image a CNN slides over the image...
+
+The result is that the neural network trains faster..
+
+\section{Bayesian Neural Networks}
+
+Bayesian neural networks take the
+
+\subsection{Bayesian Conolutional Neural Networks}
+
+Same principle...
 
@@
 
-We use a bayesian convolutional neural network implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ...
-\cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}
+We use a BCNN implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}
+
+\subsection{CIFAR-10}
+
+	\begin{figure}H
+		\centering
+	\includegraphics[width=.75\textwidth]{../Images/cifar-10.png}
+	\caption{Example CIFAR-10 images \cite{cifar10}}
+\end{figure}
+
+The CIFAR-10 dataset...
+
+\subsection{Hyperparamaters}
+
+We used the following hyperparamaters for training
+	\begin{center}
+		\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
+			\hline
+			\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
+			\hline\hline
+			Epochs & 500 & 500\\
+			\hline
+			Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
+			\hline
+			Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
+			\hline
+			Optimizer & Adamw  & Adamw  \\
+			\hline
+		\end{tabular}
+	\end{center}
+
+\subsection{Results}
 

### 2024-04-01 Paper/paper.tex
updated

@@
 \usepackage{rotating}
+\usetikzlibrary{positioning,shapes.multipart}
 
@@
 
+Neural networks are made out of a series of neurons. 
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}[
+		neuron/.style={
+			circle,
+			draw,
+			minimum size=1.5em,
+			inner sep=0pt,
+		},
+		font=\footnotesize,
+		>=latex
+		]
+		% Draw the neuron
+		\node [neuron] (neuron) at (0,0) {$\Sigma$};
+		% Draw the input nodes and labels
+		\foreach \i/\txt in {1/$x_1$,2/$x_2$,3/$x_n$} {
+			\node [neuron,left=of neuron] (input\i) at (-1.5,-\i +2) {\txt};
+			\draw[->] (input\i) -- node[above] {} (neuron);
+		}
+		% Draw the bias node and label
+		\node [neuron,left=of neuron] (bias) at (1.25,1) {Bias};
+		\draw[->] (bias) -- node[right] {} (neuron);
+		% Draw the activation function label
+		\node[align=center,below right =0.5em of neuron] {Activation \\ function};
+		% Draw the output node and label
+		\node [neuron,right=of neuron] (output) at (1.5,0) {Output};
+		\draw[->] (neuron) -- node[above] {} (output);
+		% Draw the relevant functions
+		%\draw[->] (0,-1.5) -- (0,-2.5) node[midway,right] {Weighted sum};
+		%\draw[->] (-1.5,-3.5) -- (-1.5,-4.5) node[midway,left] {Bias};
+		%\draw[->] (1.5,-0.5) -- (1.5,-1.5) node[midway,right] {Activation};
+
+		% Draw the activation function shape
+		%\node[draw,rectangle,minimum width=2em,minimum height=2em] (actfunc) at (0,1) {};
+		%\node[above=0.1em of actfunc] {ReLU};
+
+	\end{tikzpicture}
+	\caption{Neural network neuron}
+\end{figure}
+
 \subsection{Convolutional Neural Networks }
@@
 
-Bayesian neural networks take the
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=.55\textwidth]{../Images/example_bnn.png}
+	\caption{Example BNN  \cite{FleszarBNN}}
+\end{figure}
+
+Bayesian neural networks take the same principle as
+
+Similar to a Neural network such as...
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=.55\textwidth]{../Images/BNN-neuron.png}
+	\caption{Example BNN Neuron \cite{hase2019machine}}
+\end{figure}
 
@@
 
-	\begin{figure}H
+	\begin{figure}[H]
 		\centering
@@
 
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
+		\caption{CNN}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.9\linewidth]{../Images/BNN_confusion_matrix}
+		\caption{BCNN}
+	\end{subfigure}
+	\caption{Confusion matrices}
+\end{figure}
+
 \section{Closing}

### 2024-04-02 Paper/paper.tex
Updated notebook

@@
 	\caption{Example neural network}
+	\label{fig:example-nn}
 \end{figure}
 
-Neural networks....
+A neural network takes a series of inputs... In figure \ref{fig:example-nn}, the network takes two inputs, has one hidden layer of size
 
-Neural networks are made out of a series of neurons. 
 \begin{figure}[H]
@@
 		% Draw the input nodes and labels
-		\foreach \i/\txt in {1/$x_1$,2/$x_2$,3/$x_n$} {
-			\node [neuron,left=of neuron] (input\i) at (-1.5,-\i +2) {\txt};
-			\draw[->] (input\i) -- node[above] {} (neuron);
+		\foreach \i/\txt in {1/$1$,2/$2$,3/$n$} {
+			\node [neuron,left=of neuron] (input\i) at (-1.5,-\i +2) {x\txt};
+			\draw[->] (input\i) -- node[above] {$w$\txt} (neuron);
 		}
@@
 	\caption{Neural network neuron}
+	\label{fig:neuron}
 \end{figure}
+
+Neural networks are made out of a series of neurons...
+The neurons take a set of inputs, multiplies the inputs by the weights, sums the weighted input, adds a bias, and runs the output through an activation function...
 
@@
 	\caption{CNN pipeline \cite{eli5CNN}}
+	\label{fig:cnn-pipeline}
 \end{figure}
 
-Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition. Instead of reading the entire image a CNN slides over the image...
+Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition.
+While this might sound like a seperate model structure, CNNs are largely the same.
+In figure \ref{fig:cnn-pipeline} the difference between a traditional neural network is the convolutional layer.
+Instead of reading the entire image at once, a convolutional layer slides over the image...
 
-The result is that the neural network trains faster..
+IMAGE OF SLIDING (gif split)
+
+ ...
 
@@
 
-\subsection{Bayesian Conolutional Neural Networks}
+\subsection{Bayesian Convolutional Neural Networks}
 
-Same principle...
+Bayesian convolutional neural network (BCNN) are similar to CNNs. The difference between is that BCNNs and a CNN is that the BCNN uses a bayesian neuron.
 
@@
 
-The CIFAR-10 dataset...
+The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set.
+It contatins 60,000 $16 \times 16$ RGB pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}.
+It is used...
 
@@
 
-We used the following hyperparamaters for training
+We used the following hyperparamaters for training:
+\begin{figure}[H]
 	\begin{center}
@@
 \end{center}
+\end{figure}
+
+In addition to the above, the two models have the same number of levels...
 
@@
 
+The two have roughly similar accuracies given the model
+
 \section{Closing}

### 2024-04-02 Paper/paper.tex
Updated paper

@@
 
-\section{Neural Network}
+\section{Machine Learning}
+
+% To understand the concept of deep learning, we first need to understand the broader area it is considered a subset of; machine learning. 
+Machine learning is considered to be a branch of artificial intelligence (AI) with the goal to help AI “learn” more, but specifically in a way that imitates the human process of learning through the use of data and algorithms\cite{ibmWhatIsML}.
+The term supervised learning refers to what one most commonly thought of methods of employing this practice, which consists of using a labeled dataset to train, or get an algorithm to learn, how to predict outcomes and/or classify data correctly.
+This process can be broken down into three major steps, which include a decision process, an error function, and an updating or optimization process \cite{berkelyWhatIsML}.
+In the first step, the decision process includes exactly what it sounds like; the decision process of the algorithm.
+This is the set of steps the algorithm takes after receiving the data based on the goal of the model.
+The second step in the process is the error function, which is the method of measuring chosen to see if the algorithm gave a “good” or “bad” input.
+The two most common choices of the error function is a simple yes or no on if a data point was classified correctly, or the difference in value between the predicted outcome and the actual observed outcome.
+Finally, the third and last step is what is considered to be the actual learning part of the process.
+This step, the updating or optimization process, requires the algorithm to review the past data and outputs of the error function in order to better correct its decision making process in the future.
+
+Throughout this report, we’ll often use the terms machine learning, deep learning, and neural networks.
+It is important to note that although these are fundamentally related fields, deep learning is a subfield of neural networks, and in turn, neural networks are a subfield in machine learning.
+Thus when we are looking at Bayesian neural networks, we are looking at a subfield of more general neural networks, and that Bayesian neural networks are a subfield of a subfield of machine learning.
+
+% EDIT THIS SECTION But, back to deep learning!
+What sets deep learning apart from the more general machine learning is that unlike the supervised learning process that was described before, deep learning does not necessarily have to use pre labelled data sets.
+It can, if required, but the point of a deep learning algorithm is that one feature of the algorithm is that it itself can distinguish between the different types of data purely by looking at the data.
+This process of built in categorical distinction is extremely helpful, as it limits human interaction and interventions that are required in the learning process, as large amounts of data do not need to be “processed by hand” in order for the algorithm to make use of them (2).
+Deep learning models work through a “layering” process, where multiple layers of the original three steps listed above work together in the algorithmic process.
+
+\subsection{Neural Network}
 

### 2024-04-03 Paper/paper.tex

--- 2024-04-02 Paper/paper.tex
@@
 
-\subsection{History}
+\section{Machine Learning}
 
-\begin{figure}[H]
-	\begin{tikzpicture}[scale=0.5,every node/.style={outer sep=5pt}]
-		%Notation: {year, the title of the event}
-		%NOTE! Everyting is zero-based
-		\def\ourInfo{{
-				{"1987"," The patent a 'Method of providing digital signatures' is filed by Ralph C. Merkle\cite{merkle-patent}."},
-				{"1999","The original patent expires."},
-				{"2009","Bitcoin uses Merkle Trees for 'block header commitment.'\cite{friedenbach_alm_2017}"},			
-				{"2009","BitTorent uses Merkle Trees for data integrity\cite{bep30}."},
-		}}
-		\pgfmathsetmacro{\length}{3}% Zero based.
+% To understand the concept of deep learning, we first need to understand the broader area it is considered a subset of; machine learning. 
+%Machine learning is considered to be a branch of artificial intelligence (AI) with the goal to help AI “learn” more, but specifically in a way that imitates the human process of learning through the use of data and algorithms\cite{ibmWhatIsML}.
+Machine learning includes a variety of topics of which artifical intelligence (AI) and neural networks are a subset.
+Neural networks in particular involve an abstract imitation of the human brain using simulated neurons which is trained on data using particular algorithms.
 
-		% Loop through the array containing all events.
-		\foreach \i in {0, ..., \length}{
-			\pgfmathsetmacro{\year}{\ourInfo[\i][0]}% Get the left cell (year)
-			\pgfmathsetmacro{\eventName}{\ourInfo[\i][1]}% Get the right cell (event name)
-			\draw[thick,red] (0,-2*\i-2)--(0,-2*\i);% Draw vertical line
-			\ifnum \i=0 % Should be in red text
-			\draw(0,-2*\i-1) node[black, right, align = left]{\eventName};% Display the event name
-			\draw(0,-2*\i-1) node[black, left] {\year};
-			\else % Should be in black text
-			\draw(0,-2*\i-1) node[right, black]{\eventName};% Display the event name
-			\draw(0,-2*\i-1) node[left] {\year};% Display the year
-			\fi
-		}
-		% Draw the bullet with the dash
-		\foreach \i in {0, ..., \length}{
-			\filldraw[draw = white, fill = red,thick] (0,-2*\i-1) circle (5pt);
-			\draw[thick,red] (-12pt,-2*\i-1)--(0,-2*\i-1);
-		}
-	\end{tikzpicture}
-\end{figure}
+The term supervised learning refers to a specific common method of machine learning which uses a labeled dataset to train a model to correctly predict the labels via some training algorithm.
+A classification problem in supervised learning involves predictions where all labels are grouped into a set of categories.
+The training process can be broken down into three major steps, which include a decision process, an error function, and an optimization process \cite{berkelyWhatIsML}.
+The decision process is the set of steps the algorithm takes after receiving the data based on the goal of the model.
+The second step in the process is the error function, which is the method of measuring chosen to see if the algorithm gave a “good” or “bad” input.
+The two most common choices of the error function is a simple yes or no on if a data point was classified correctly in the case of classification, or the difference in value between the predicted outcome and the actual observed outcome for continuous values.
+Finally, the third and last step is the part of the process that implements learning.
+This step, the updating or optimization process, requires the algorithm to review the past data and outputs of the error function in order to better correct its decision making process in the future.
 
-\section{Neural Network}
+Throughout this report, we’ll often use the terms machine learning, deep learning, and neural networks.
+It is important to note that although these are fundamentally related fields, deep learning is a subfield of neural networks that in particular focuses on more complicated neural networks, while neural networks are a subfield in machine learning.
+
+We will be training a classifier on labeled images in a supervised learning process to predict what is depicted in the image from a range of possibilities such as dog, cat, and plane.
+
+% EDIT THIS SECTION But, back to deep learning!
+What sets deep learning apart from the more general machine learning is that unlike the supervised learning process that was described before, deep learning does not necessarily have to use pre labelled data sets.
+It can, if required, but the point of a deep learning algorithm is that one feature of the algorithm is that it itself can distinguish between the different types of data purely by looking at the data.
+This process of built in categorical distinction is extremely helpful, as it limits human interaction and interventions that are required in the learning process, as large amounts of data do not need to be “processed by hand” in order for the algorithm to make use of them (2).
+Deep learning models work through a “layering” process, where multiple layers of the original three steps listed above work together in the algorithmic process.
+
+\subsection{Neural Network}
 

### 2024-04-16 Paper/paper.tex
Added stuff on BNN and CIFAR10

@@
 	\and
-	Sorgmon, Ava
+	Sorgman, Ava
 	\and
-	Conor
+	Bekaert, Conor
 }
@@
 
-The term supervised learning refers to a specific common method of machine learning which uses a labeled dataset to train a model to correctly predict the labels via some training algorithm.
+The term supervised learning refers to a specific common method of machine learning that uses a labeled dataset to train a model to correctly predict the labels via some training algorithm.
 A classification problem in supervised learning involves predictions where all labels are grouped into a set of categories.
@@
 The decision process is the set of steps the algorithm takes after receiving the data based on the goal of the model.
-The second step in the process is the error function, which is the method of measuring chosen to see if the algorithm gave a “good” or “bad” input.
-The two most common choices of the error function is a simple yes or no on if a data point was classified correctly in the case of classification, or the difference in value between the predicted outcome and the actual observed outcome for continuous values.
+The second step in the process is the error function, which is the method of measuring chosen to see if the algorithm gave a ``good" or ``bad" input.
+The two most common choices of the error function are a simple yes or no on whether a data point was classified correctly in the case of classification, or the difference in value between the predicted outcome and the actual observed outcome for continuous values.
 Finally, the third and last step is the part of the process that implements learning.
-This step, the updating or optimization process, requires the algorithm to review the past data and outputs of the error function in order to better correct its decision making process in the future.
+This step, the updating or optimization process, requires the algorithm to review the past data and outputs of the error function in order to better correct its decision-making process in the future.
 
-Throughout this report, we’ll often use the terms machine learning, deep learning, and neural networks.
+Throughout this report, we will often use the terms machine learning, deep learning, and neural networks.
 It is important to note that although these are fundamentally related fields, deep learning is a subfield of neural networks that in particular focuses on more complicated neural networks, while neural networks are a subfield in machine learning.
@@
 We will be training a classifier on labeled images in a supervised learning process to predict what is depicted in the image from a range of possibilities such as dog, cat, and plane.
+These images come from the CIFAR-10 dataset, which will be discussed more in detail later in this paper.
 
@@
 
-Bayesian neural networks take the same principle as
+Bayesian neural networks (BNN) take the same principle as your typical neural network, but factor in a measure of uncertainty into the prediction of the network.
+This uncertainty, of course, comes from the Bayesian theory of statistics, which believes that all events have some level of randomness, and thus must have uncertainty in their prediction.
+
+One way this uncertainty can be built into the model is through a prior probability distribution.
+Uncertainty estimates of the model can be obtained from the parameters of the BNN in their probability distributions \cite{shridhar2019comprehensive}.
+The average estimate of the parameters is computed through multiple different models during the training process, which can regularize the network.
+However, it can be very difficult to calculate the model posterior of a BNN.
+Approximations of the posterior of the model are most often used, but those are often still very computationally intensive.
+Different methods of approximating the model's posterior is a current research topic within the field.
+
+The two main types of uncertainty within a BNN are aleatoric uncertainty and epistemic uncertainty.
+Aleatoric uncertainty is a measure of the uncertainty in the observations, which is uncertainty that is inherent in any form of data.
+This type of uncertainty is modeled by placing a prior distribution over the output of the BNN model.
+In contrast, epistemic uncertainty is a measure of the uncertainty caused by the model and its predictions.
+It is modeled by a prior distribution over the model's weights, and an analysis of how much the weights of the model change when the data given to the model changes \cite{shridhar2019comprehensive}.
+
+But what is so great about calculating uncertainty in our model?
+Well, it's that our predictions become more uncertain.
+One of the major issues with neural networks as they are is they are highly prone to overfitting the data.
+Although they are great at predictions on the training data they are given, they often struggle with predictions on the testing data they are given due to the issue of overfitting.
+Many methods have been developed in order to regularize neural networks to work to prevent this from occurring, such as weight control measures.
+Using the Bayesian framework of uncertainty and building it into a model serves as a built-in prevention of overfitting.
 
@@
 
-The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set.
-It contatins 60,000 $16 \times 16$ RGB pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}.
-It is used...
+The CIFAR-10 (Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set.
+It contains $60,000$ $32 \times 32$ RGB pictures of airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks \cite{cifar10}.
+The ten classes within the dataset are mutually exclusive, meaning there is no image containing multiple of the objects mentioned above.
+The number of images is split evenly between each class, with $6,000$ images per each type of object.
+It is a very popular data set (in fact the most common) to use in machine learning and training neural networks, due to the extensive size, as well as the decent number of categories.
+The purpose of the images within the dataset being of a lower resolution is to allow researchers to see more quickly (and with less computation effort) how well an algorithm works on classification with the dataset.
+Convolutional neural networks are often seen to be the ``best" at classifying CIFAR-10.
 

### 2024-04-16 Paper/paper.tex
Updated models and paper

--- 2024-04-03 Paper/paper.tex
@@
 \usetikzlibrary{positioning,shapes.multipart}
+ \usepackage{listings}
 
@@
 
-A neural network takes a series of inputs... In figure \ref{fig:example-nn}, the network takes two inputs, has one hidden layer of size
+A neural network takes a series of inputs. An example of a neural network with two inputs, one hidden layer of size three, and two outputs appears in figure \ref{fig:example-nn}
+
+\subsection{Neural Network Neurons}
 
@@
 
- ...
-
 \section{Bayesian Neural Networks}
@@
 
-Bayesian neural networks take the same principle as
+Bayesian neural networks operate the same way as a normal
 
-Similar to a Neural network such as...
+\subsection{Bayesian Neural Network Neuron}
+
+Similar to a neural network such as...
 
@@
 \end{figure}
+
+\subsubsection{Priors}
+
+This section was requested by Micheal.
 
@@
 
-The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set.
-It contatins 60,000 $16 \times 16$ RGB pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}.
-It is used...
+The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a popular machine learning  dataset set.
+It contatins 60,000 $16 \times 16$ color pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}.
+Because of its simple task and variety of images, it is often used as a baseline task for new  model structures.
 
@@
 	\hline\hline
-		Epochs & 500 & 500\\
+	Epochs & 100 & 100\\
 	\hline
-		Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
+	Learning Rate & 0.001  & 0.003  \\
 	\hline
-		Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
+	Regularization Rate& 0.001 & 0.001 \\
 	\hline
@@
 
-In addition to the above, the two models have the same number of levels...
+In addition to the hyperparamaters above, the two models have the same number of layers and levels.
+We did not adjust the priors, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.
 
 \subsection{Results}
+
+\begin{figure}[H]
+	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
+		\hline
+		\textbf{Metric} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
+		\hline\hline
+		Train Accuracy & 84.96\% & 81.27\%\\
+		\hline
+		Validation Accuracy & 61.76\%  & 59.21\%  \\
+		\hline
+		Time to Train & 16 min 11 sec  & 22 min 11 sec  \\
+		\hline
+	\end{tabular}
+\end{figure}
+
+The results we achieved with training were about the same between the BCNN and the CNN. However, the bayesian model took longer to train.
 
@@
 		\centering
+		\includegraphics[width=\linewidth]{../Images/CNN_val_acc_over_time}
+		\caption{CNN}
+	\end{subfigure}% //  
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../Images/BNN_val_acc_over_time}
+		\caption{BCNN}
+	\end{subfigure}
+	\caption{Train vs validation accuracy over time}
+	\label{fig:train-v-val}
+\end{figure}
+
+Additionally, neither model converged with the train and validation accuracy, this is an indication that we might need to increase the regularization rate.
+Another thing to note from figure \ref{fig:train-v-val} is that the BCNN took longer to divirge from the train accuracy.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{\textwidth}
+		\centering
 		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
 		\caption{CNN}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
+	\end{subfigure} \\% //  
+	\begin{subfigure}{\textwidth}
 		\centering
@@
 
-The two have roughly similar accuracies given the model
+The two models have the same set of confusions
 

### 2024-04-16 Paper/paper.tex

--- 2024-04-16 Paper/paper.tex
@@
 
-Similar to a Neural network such as...
+\subsection{Bayesian Neural Network Neuron}
+
+Similar to a neural network such as...
 

### 2024-04-17 Paper/paper.tex
Added drafts of Conor's sections
Added to/wrote Neural Networks, Neural Network Neurons, CNNs, BNNs, BBNN Neurons, Priors, and BCNNs

@@
 
-A neural network takes a series of inputs. An example of a neural network with two inputs, one hidden layer of size three, and two outputs appears in figure \ref{fig:example-nn}
+There are many effective introductions to neural networks to any level of detail available elsewhere, so we will present a straightforward summary of the concepts required for understanding the work of this paper.
+
+Many models for analyzing data involve making an assumption about the functional form of the outputs given the inputs or predictors.
+Neural networks are no exception - at the most basic conceptual level, a neural network is just a really complicated function that has the potential to represent many patterns and dimensions through its complexity.
+Their name comes from the inspiration they take from the human brain, the idea that enough neurons with enough connections between them can encode everything needed for effective predictions.
+Indeed, the fundamental unit of a neural network is a neuron with its associated connections.
+
+Neural networks are typically organized in a series of layers of many neurons, where each individual neuron of one layer is connected to every neuron of the previous layer.
+Data flows from an initial input layer, through hidden layers, then into the outputs as visualized in Figure \cite{fig:example-nn}.
+The connections are assigned certain weights, which measure the influence of a neuron on the next layer.
+This structure ultimately yields a complicated yet well-defined function because every step is a clearly-defined arithmetic operation, and they are all composed into a single whole.
+Neural networks can have different architectures depending on the organization and types of layers involved.
 
 \subsection{Neural Network Neurons}
+
+As shown in Figure \ref{fig:neuron}, any single neuron is connected to the neurons $x_1, x_2, ..., x_n$ from the previous layer.
+The outputs of the previous neurons become the inputs to the new neuron by means of connections with weights $w_1, w_2, ..., w_n$ associated with them (each previous neuron has a certain weight).
+The neuron itself first takes a value calculated as a weighted sum $\sum_i w_i x_i$ of the inputs $x_i$ to it, then typically an additive bias is included.
+Lastly, the value is passed through an activation function which restricts the value to a certain range, typically $[0,1]$.
+
+The weights and the biases of a neural network are the parameters, and they are the values that are tuned in the training process.
+In a sense, they represent the "memory" of the network, whatever it has learned from training.
+For any particular network architecture (meaning the choice of types of layers and their order), once the model has been trained with a particular architecture, the parameters are all you need to run that network on new data to make predictions.
 
@@
 
-Neural networks are made out of a series of neurons...
+%Neural networks are made out of a series of neurons...
 The neurons take a set of inputs, multiplies the inputs by the weights, sums the weighted input, adds a bias, and runs the output through an activation function...
@@
 Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition.
-While this might sound like a seperate model structure, CNNs are largely the same.
-In figure \ref{fig:cnn-pipeline} the difference between a traditional neural network is the convolutional layer.
-Instead of reading the entire image at once, a convolutional layer slides over the image...
+While this might sound like a separate model structure, CNNs are largely the same.
+The primary difference from a traditional neural network is the convolutional layer, as highlighted in Figure \cite{fig:cnn-pipeline}.
+Instead of reading the entire image at once, a convolutional layer slides a small window over the image, shrinking that window even further by the application of a convolution operation.
+Once the window has slid over the entire image, a downsized image is formed that may encode useful information more densely.
+Because of this downsizing action, CNNs typically require fewer parameters relative to the traditional neural networks described previously, which improves training costs and the capabilities of the model.
 
-IMAGE OF SLIDING (gif split)
+%IMAGE OF SLIDING (gif split)
 
@@
 
+A Bayesian neural network introduces priors on the parameters $\theta$ of a neural network and uses the data to adjust these priors to reach posterior distributions for these parameters.
+Recall that a (trained) neural network is really just determined by its parameters - the weights and biases.
+This gives rise to the conceptual interpretation that a Bayesian neural network is an infinite ensemble of possible neural networks which can be sampled to obtain any number of individual networks.
+%(... could talk about how this enables comparison between networks, uncertainty, etc)
+
+Constructing a Bayesian neural network involves selecting a model architecture and choosing the priors, which are also known as the "stochastic model" in this context.
+The definition of Bayesian neural networks provides flexibility, since the primary difference is that neuron weights get distributions instead of individual values.
+As a result, most model architectures that work for a typical neural network also work for a Bayesian version of that network.
+Lastly, the training of a Bayesian neural network uses techniques such as MCMC for inference.
+
 \subsection{Bayesian Neural Network Neuron}
 
-Similar to a neural network such as...
+A visualization of a Bayesian neuron appears in Figure \ref{fig:bnn-neuron}.
+It is in fact quite similar to Figure \ref{fig:neuron}, with the essential difference that the individual values from before have been replaced with distributions.
+Within a neuron, the distributions from input neurons are weighted by the weight distributions and combined together along with the bias distribution.
+After passing through the activation function, the neuron output is produced.
 
@@
 	\caption{Example BNN Neuron \cite{hase2019machine}}
+	\label{fig:bnn-neuron}
 \end{figure}
@@
 
-This section was requested by Micheal.
+The Bayesian paradigm requires a prior on the parameters of a neural network to facilitate training.
+However, making choice of a prior on all the parameters of a network, following anything other than a simple concept, is difficult, especially given the limited understanding of how priors at one layer affects the next in general.
+For the purposes of this work, only one prior-selection scheme will be considered, since considering many methods would require introducing many further new concepts.
+
+A choice of prior that is both commonly used and intuitive is an independent normal distribution on each weight.
+In particular, a $\mathcal{N}(0, \sigma^2)$ distribution with zero mean and some standard deviation $\sigma$ for each particular weight typically works.
+This can be thought of as a reasonable choice of vague prior.
+Since further interpretation of how these priors influence the model becomes even more complicated for other priors, selecting a more informative prior would be tricky.
+For an example of this complexity, Vladimirova et al.
+contend that for a network with these priors whose activation functions satisfying a certain "extended envelope property", the priors on the $k^{th}$ hidden layer become sub-Weibull-distributed with parameter $k/2$ conditional on the data passing through the network.
+Such interpretation is valuable, but beyond the scope of this paper.
+
+However, it turns out there is suggestive parallel between a prior in a Bayesian neural network and regularization in a typical neural network.
+Regularization is an additional term in the loss that penalizes large weights.
+Intuitively, this helps resist overfitting by preventing a single neuron from overly influencing the model, since such a neuron may be overemphasizing a fluke of the training set rather than a general pattern.
+The regularization term typically takes the form $\alpha ||w||_p$  where $||\cdot||_p$ is some choice of metric on $R^n$, typically $p=1$ (Manhattan/taxicab distance) or $p=2$ (Euclidean distance), and $\alpha$ is the regularization hyperparameter that controls how strongly large weights are penalized.
+
+As in Jospin et al., consider network parameters $\theta$ with a loss function $L$ assumed to be the negative log likelihood loss, where $D_y$ represents the true labels for the training data $D_x$.
+Suppose the network does not use regularization.
+Maximum likelihood estimation aims to find the choice of $\theta$ which minimizes the loss on the given data:
+$$
+\hat{\theta} = \arg \min_{\theta} \left\{ L_{D_x, D_y} (\theta) \right\}.
+$$
+From the Bayesian perspective, since the negative log likelihood loss is used, this means that
+$$
+\hat{\theta} = \arg \min_{\theta} \left\{- \log P(D_y|D_x, \theta) \right\} = \arg \max_{\theta} \left\{ P(D_y|D_x, \theta) \right\}.
+$$
+This formula indicates to find the choice of $\theta$ that maximizes the probability of the true labels $D_y$ for the data given the observed $D_x$ values for parameters $\theta$.
+Now, suppose a prior $p(\theta)$ is introduced:
+$$
+\hat{\theta} = \arg \max_{\theta} P(D_y|D_x, \theta) p(\theta).
+$$
+When converted back to the frequentist paradigm under log-likelihood loss, the multiplicative factor for the prior becomes an additive regularization term:
+$$
+\hat{\theta} = \arg \min_{\theta} L_{D_x, D_y} (\theta) + reg(\theta), \quad reg(\theta) = -\log(p(\theta)).
+$$
+Jospin et al.
+state that normal prior selected above is "equivalent to a weighted $\ell_2$ regularization (with weights $1/\sigma$) when training a point estimate network." In this sense, the Bayesian model which utilizes priors specified in advance helps prevent overfitting simply by including priors in the first place.
 
@@
 
-Bayesian convolutional neural network (BCNN) are similar to CNNs. The difference between is that BCNNs and a CNN is that the BCNN uses a bayesian neuron.
+As discussed previously, Bayesian neural networks work with most functional models that work for typical neural networks.
+Convolutional neural networks are no exception - by simply replacing typical CNNs with Bayesian counterparts containing Bayesian neurons and the appropriate operations, a Bayesian convolutional neural network (BCNN) is created.
 

### 2024-04-18 Paper/paper.tex
Updated report

@@
 \tableofcontents
-
-\section{Introduction}
 
@@
 
-We used the following hyperparamaters for training:
+We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparamaters seperately.
+We did not adjust the priors on the BCNN, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.
+We found the following hyperparemeters to created the best model:
+
 \begin{figure}[H]
@@
 \end{figure}
-
-In addition to the hyperparamaters above, the two models have the same number of layers and levels.
-We did not adjust the priors, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.
 
@@
 
-Additionally, neither model converged with the train and validation accuracy, this is an indication that we might need to increase the regularization rate.
-Another thing to note from figure \ref{fig:train-v-val} is that the BCNN took longer to divirge from the train accuracy.
+Based on the divergent lines in figure \ref{fig:train-v-val}, the model needs tuning.
+Specifically, the regularization rate needs to be raised.
+One interesting thing that appears in the figures, is that the BCNN took longer to diverge from the train accuracy compared to CNN.
 
@@
 	\caption{Confusion matrices}
+	\label{fig:confusion}
 \end{figure}
 
-The two models have the same set of confusions
-
-\section{Closing}
+Based on the confusion matrix from two models in \ref{fig:confusion}, the two models confuse similar sets of classes.
+Both models struggle to differentiate animals, but the BCNN has poorer accuracy on the classes that are easily confused.
 

### 2024-05-06 Paper/paper.tex
Finished presentation bullets in slides
Also made slight fix to paper
Updated conclusion
Buffed neural network discussion
Added lots of neural network discussion, including mathematical details, finishing Michael's first point of feedback.
Slightly edited/improved BNN discussion.

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage{subcaption}
@@
 \pagestyle{fancy} % Default page style 
-\lhead{Blair, Sorgman, Conor}
+\lhead{Blair, Sorgman, Bekaert}
 \chead{}
@@
 
-\subsection{Neural Network}
+\subsection{Introduction to Neural Networks}
 
@@
 
-There are many effective introductions to neural networks to any level of detail available elsewhere, so we will present a straightforward summary of the concepts required for understanding the work of this paper.
+There are many effective introductions to neural networks to any level of detail available elsewhere, but we will present a summary of the core concepts here.
 
 Many models for analyzing data involve making an assumption about the functional form of the outputs given the inputs or predictors.
-Neural networks are no exception - at the most basic conceptual level, a neural network is just a really complicated function that has the potential to represent many patterns and dimensions through its complexity.
+Neural networks are no exception - at the most basic conceptual level, a neural network is just a really complicated function that has the potential to represent many patterns through its complexity.
 Their name comes from the inspiration they take from the human brain, the idea that enough neurons with enough connections between them can encode everything needed for effective predictions.
-Indeed, the fundamental unit of a neural network is a neuron with its associated connections.
+Indeed, the fundamental unit of a neural network is a neuron and its associated connections.
 
@@
 The connections are assigned certain weights, which measure the influence of a neuron on the next layer.
-This structure ultimately yields a complicated yet well-defined function because every step is a clearly-defined arithmetic operation, and they are all composed into a single whole.
-Neural networks can have different architectures depending on the organization and types of layers involved.
+The next section will describe the structure of neurons in a linear layer, which is a typical type of layer.
+%This structure ultimately yields a complicated yet well-defined function because every step is a clearly-defined arithmetic operation, and they are all composed into a single whole.
+%Neural networks can have different architectures depending on the organization and types of layers involved.
 
@@
 
-As shown in Figure \ref{fig:neuron}, any single neuron is connected to the neurons $x_1, x_2, ..., x_n$ from the previous layer.
+% As shown in Figure \ref{fig:neuron}, any single neuron is connected to the neurons $x_1, x_2, ..., x_n$ from the previous layer.
 The outputs of the previous neurons become the inputs to the new neuron by means of connections with weights $w_1, w_2, ..., w_n$ associated with them (each previous neuron has a certain weight).
@@
 
-The weights and the biases of a neural network are the parameters, and they are the values that are tuned in the training process.
+%The weights and the biases of a neural network are the parameters, and they are the values that are tuned in the training process.
 In a sense, they represent the "memory" of the network, whatever it has learned from training.
@@
 
-%Neural networks are made out of a series of neurons...
-The neurons take a set of inputs, multiplies the inputs by the weights, sums the weighted input, adds a bias, and runs the output through an activation function...
+A neural network neuron in a linear layer is, in practice, a varying real scalar value.
+The value is produced from the values $X = (x_1, ..., x_n)$ of the neurons in the previous layer by taking the dot product of $X$ with the weight parameters $W = (w_1, ..., w_n)$, plus an additive bias $b$.
+This weighted sum $X \cdot W + b$ is then passed through some activation function $\text{Act}(\cdot)$ which applies a nonlinear transformation to improve efficiency.
+As such, the action of a particular layer on the previous layer's neurons to produce the next value can be characterized as $X_{i+1} = \text{Act}(X_{i} \cdot W_{i} + b_{i})$.
+Typical activation functions include the Rectified Linear Unit (ReLU) defined by $\text{ReLU}(x) = \max (0, x)$ and the sigmoid, $\sigma(x) = \frac{1}{1 + e^{-x}}$.
+
+This process can be generalized to an entire layer at once via matrix multiplication (which encodes the dot product), and this also improves efficiency.
+These layers are nested interatively to the depth of the network - for example, a network with three linear layers could take the form
+$$
+	\text{ReLU}(\text{ReLU}(\text{ReLU}(x \times W_1 + b_1) \times W_2 + b_2) \times W_3 + b_3).
+$$
+A network architecture is generally defined by the depth (number of layers), the number of neurons/parameters in the layers, and the type of layer used.
+
+\subsection{Neural Network Training}
+
+To train a neural network requires a loss function $L$, such as the MSE or the cross-entropy loss (cross-entropy loss is essentially the log-likelihood loss from frequentist maximum likelihood estimation).
+An optimization process, typically a variant of stochastic gradient descent, adjusts the neural network parameters $\beta$ (the weights $W$ and biases $b$) to minimize this loss on the provided data.
+Stochastic gradient descent updates the parameters at each step by the formula
+$$
+\beta_{n+1} = \beta_n - \alpha (\nabla \ell(x_s, y_s, \beta)),
+$$
+where $\alpha$ is the learning rate (how quickly parameter adjustments are made).
+Minimization is implemented using a stochastic approximation of the gradient of the loss (hence the name stochastic gradient descent).
+The true loss $L(\beta)$ on the whole dataset $x, y$ is approximated via an averaged estimate $\ell(x_s, y_s, \beta)$ on a subset $(x_s, y_s)$ of the data.
+Gradients are calculated via \textit{backpropagation}, which is beyond the scope of this discussion, but essentially consists of iterated application of the chain rule.
+
+Each step of training is called an \textit{epoch}.
+In each epoch, the data passes through the network, the gradients are approximated via backpropagation, and the parameters are updated with this approximation.
+These parameters, matrices of weights and biases, \textit{are} the network once it is trained - they represent the "memory" of the network, whatever it has learned from the training data.
+Predictions are obtained as the outputs after passing new data through the same network architecture with these weights and biases specified.
+This is a "black box" model because there is no clear interpretation of the giant matrices of parameters - in the end, they're just floating-point numbers.
 
@@
 
-Bayesian neural networks (BNN) take the same principle as your typical neural network, but factor in a measure of uncertainty into the prediction of the network.
+Bayesian neural networks (BNN) are similar in principle to typical neural networks, but represent uncertainty in the predictions of a neural network by assigning probability distributions to the parameter (weight and bias) values and updating these distributions.
+This follows Bayesian principles, where rather than producing a single estimated value as in typical neural networks, the "evidence" provided by the data updates a distribution of possible true values.
+
+% take the same principle as your typical neural network, but factor in a measure of uncertainty into the prediction of the network.
 This uncertainty, of course, comes from the Bayesian theory of statistics, which believes that all events have some level of randomness, and thus must have uncertainty in their prediction.
 
-One way this uncertainty can be built into the model is through a prior probability distribution.
-Uncertainty estimates of the model can be obtained from the parameters of the BNN in their probability distributions \cite{shridhar2019comprehensive}.
+Uncertainty can be built into these models through prior probability distributions. 
+%Uncertainty estimates of the model can be obtained from the parameters of the BNN in their probability distributions \cite{shridhar2019comprehensive}. 
 The average estimate of the parameters is computed through multiple different models during the training process, which can regularize the network.
@@
 
-But what is so great about calculating uncertainty in our model?
-Well, it's that our predictions become more uncertain.
+But what is so great about calculating uncertainty in our model? %Well, it's that our predictions become more uncertain. 
 One of the major issues with neural networks as they are is they are highly prone to overfitting the data.
@@
 Many methods have been developed in order to regularize neural networks to work to prevent this from occurring, such as weight control measures.
-Using the Bayesian framework of uncertainty and building it into a model serves as a built-in prevention of overfitting.
+The Bayesian framework, and particularly the choice of prior distributions, builds this into the model, which helps prevent overfitting.
+%Using the Bayesian framework of uncertainty and building it into a model serves as a built-in prevention of overfitting.
 
-A Bayesian neural network introduces priors on the parameters $\theta$ of a neural network and uses the data to adjust these priors to reach posterior distributions for these parameters.
+%A Bayesian neural network introduces priors on the parameters $\theta$ of a neural network and uses the data to adjust these priors to reach posterior distributions for these parameters. 
 Recall that a (trained) neural network is really just determined by its parameters - the weights and biases.
@@
 As a result, most model architectures that work for a typical neural network also work for a Bayesian version of that network.
-Lastly, the training of a Bayesian neural network uses techniques such as MCMC for inference.
+%Lastly, the training of a Bayesian neural network uses techniques such as MCMC for inference.
+
+% TODO: Fill in information about how distributions are imposed on a BNN
 
@@
 \begin{figure}[H]
+	\centering
 	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed

### 2024-05-06 Paper/paper.tex
removed abstract
lol
More discussion of hyperparameters

@@
 
-\begin{abstract}
-	Bayesian Neural Networks are...
-\end{abstract}
+%\begin{abstract}
+%	Bayesian Neural Networks are...
+%\end{abstract}
 
@@
 \subsection{Neural Network Training}
+\label{subsection:neural-network-training}
 
@@
 $$
-where $\alpha$ is the learning rate (how quickly parameter adjustments are made).
+where $\alpha$ is the \textit{learning rate}, which controls how quickly parameter adjustments are made.
 Minimization is implemented using a stochastic approximation of the gradient of the loss (hence the name stochastic gradient descent).
@@
 
-% TODO: Fill in information about how distributions are imposed on a BNN
+% TODO: Fill in information about how distributions are imposed on a BNN. See other TODO with some progress at the end of the following subsection(s)
 
@@
 \subsubsection{Priors}
+\label{subsection:priors}
 
@@
 
-However, it turns out there is suggestive parallel between a prior in a Bayesian neural network and regularization in a typical neural network.
-Regularization is an additional term in the loss that penalizes large weights.
+However, it turns out there is suggestive parallel between a prior in a Bayesian neural network and \textit{regularization} in a typical neural network.
+\textit{Regularization} is an additional term in the loss that penalizes large weights.
 Intuitively, this helps resist overfitting by preventing a single neuron from overly influencing the model, since such a neuron may be overemphasizing a fluke of the training set rather than a general pattern.
 The regularization term typically takes the form $\alpha ||w||_p$  where $||\cdot||_p$ is some choice of metric on $R^n$, typically $p=1$ (Manhattan/taxicab distance) or $p=2$ (Euclidean distance), and $\alpha$ is the regularization hyperparameter that controls how strongly large weights are penalized.
+In other words, $\alpha$ is the \textit{regularization rate}.
 
@@
 
+% TODO: Add discussion of how distributions are imposed
+%\subsection{Distributions}
+
+%In order to impose distributions on the parameters of a Bayesian neural network, there must be a clearly defined procedure for producting a posterior from the prior and the data.
+
+%Gradient descent is used to minimize (the approximation of) the KL-divergence...
+
 \subsection{Bayesian Convolutional Neural Networks}
@@
 
-We use a BCNN implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}
+We use an implementation of BCNNs from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}.
+It allowed for direct substitution of Bayesian layers for deterministic neural network layers such that the same training procedure could be applied to both types of networks.
+The normal priors previously discussed are built into these custom layers in the package.
 
@@
 
-\subsection{Hyperparamaters}
+\subsection{Hyperparameters}
 
-We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparamaters seperately.
+The hyperparameters of a neural network, such as epochs, learning rate, regularization rate, are set before training to control the process and ensure the network achieves the best possible performance for its architecture.
+Epochs and learning rate were defined in Subsection \ref{subsection:neural-network-training} while the regularization rate and its connection to Bayesian network priors was introduced in \ref{subsection:priors}.
+The choice of optimizer is not relevant to and beyond the scope of this work - Adamw as selected here simply provides a marginal performance improvement.
+
+We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparameters separately.
 We did not adjust the priors on the BCNN, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.
-We found the following hyperparemeters to created the best model:
+We found the following hyperparemeters created the best model:
 
